\bibliographystyle{jplain}
\begin{thebibliography}{9}
\bibitem{fujitani15}
  藤谷宣典ら,
  隠れ状態を用いたホテルレビューのレーティング予測.
  言語処理学会第21回年次大会, 2015.
\bibitem{quoc14}
  Quoc Le et al.,
  Distributed Representations of Sentences and Documents.
  ICML 2014, 2014.
\bibitem{nal14}
  Nal Kalchbrenner et al.,
  A Convolutional Neural Network for Modelling Sentences.
  ACL 2014, 2014.
\bibitem{rie14}
  Rie Johnson et al.,
  Effective Use of Word Order for Text Categorization
  with Convolutional Neural Networks.
  NAACL 2015, 2015.
\bibitem{duyu15}
  Duyu Tang et al.,
  Learning Semantic Representation of Users and Products
  for Document Level Sentiment Classification.
  ACL 2015, 2015.
\bibitem{yoshua03}
  Yoshua Bengio et al.,
  A Neural Probabilistic Language Model.
  The Journal of Machine Learning Research 3, 2003.
\bibitem{mihai12}
  Mihai Surdeanu et al.,
  Multi-instance Multi-label Learning for Relation Extraction.
  CoNLL 2012, 2012.
\bibitem{diederik15}
  Diederik Kingma et al.,
  Adam: A Method for Stochastic Optimization.
  ICLR 2015, 2015.
\bibitem{john12}
  John Duchi et al.,
  Adaptive Subgradient Methods for Online Learning and Stochastic Optimization.
  Journal of Machine Learning Research 12, 2011.
\bibitem{ronan08}
  Ronan Collobert et al.,
  A unified architecture for natural language processing:
  Deep neural networks with multitask learning.
  ICML 2008, 2008.
\bibitem{hozumi06}
  田中穂積,
  自然言語処理 -基礎と応用-.
  電子情報通信学会.
\bibitem{takayuki15}
  岡谷貴之,
  深層学習.
  講談社.
\bibitem{hashimoto15}
  橋本和真,
  hassyGo/paragraph-vector: paragraph vector trained by negative sampling.
  https://github.com/hassyGo/paragraph-vector.
\end{thebibliography}
