\documentclass{ttithesis}

\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{scrextend}
\usepackage{setspace}
\usepackage{color}
\usepackage{tabularx}


\title{文書・文間及びカテゴリ間の関係を考慮した\\レーティング予測}
\author{12056\hspace{16ex}外山洋太}
\date{平成28年 2月}
\laboratory{知能数理研究室}



\begin{document}

\input{introduction}
\input{related_research}
\input{proposed_method}
\input{experiments}
\input{conclusion}


\section*{謝辞}
本研究において、楽天株式会社よりホテル予約サイト楽天トラベルにおける
レビューデータを使用させていただきました。
この場を借りて深く感謝致します。



\bibliographystyle{jplain}
\begin{thebibliography}{9}
\bibitem{fujitani15}
  藤谷宣典ら,
  隠れ状態を用いたホテルレビューのレーティング予測.
  言語処理学会第21回年次大会, 2015.
\bibitem{quoc14}
  Quoc Le, and Tomas Mikolov,
  Distributed Representations of Sentences and Documents.
  ICML 2014, 2014.
\bibitem{nal14}
  Nal Kalchbrenner, Edward Grefenstette, and Phil Blunsom,
  A Convolutional Neural Network for Modelling Sentences.
  ACL 2014, 2014.
\bibitem{rie14}
  Rie Johnson, and Tong Zhang,
  Effective Use of Word Order for Text Categorization
  with Convolutional Neural Networks.
  NAACL 2015, 2015.
\bibitem{duyu15}
  Duyu Tang, Bing Qin, and Ting Liu,
  Learning Semantic Representation of Users and Products
  for Document Level Sentiment Classification.
  ACL 2015, 2015.
\bibitem{yoshua03}
  Yoshua Bengio et al,
  A Neural Probabilistic Language Model.
  The Journal of Machine Learning Research 3, 2003.
\bibitem{mihai12}
  Mihai Surdeanu et al,
  Multi-instance Multi-label Learning for Relation Extraction.
  CoNLL 2012, 2012.
\end{thebibliography}

\end{document}
