Sentiment classification of product reviews are important
to analyze sentiment of them for marketing in companies.
%The present methods of sentiment classification
%on multiple categories of rating
%are not capable enough to classify sentiment of a review
%considering relations among its text, its sentences and categories.

Nowadays, on sentiment classification problem,
some methods using neural network are proposed
and work better than previous methods.
Neural network is capable to extract and utilize complex relations
among factors in input features for sentiment classification.
However, they are usually for binary or multi-class classification
on one category.

As a method to learn semantic representations of large language expressions,
such as documents, paragraphs, and sentences,
the Distributed  Memory model of Paragraph Vectors (PV-DM) is proposed
and shows good performance on sentiment classification
while it ignores order of sentences in the classification step.

This research aims to propose a method of sentiment classification
on multiples categories
which considers relations among its text, its sentences and categories
and improves classification accuracy better than present methods.

The proposed method classifies reviews in 2 steps.
First, it generates distributed representations of reviews and sentences
in them using PV-DM.
Second, it classifies reviews by them to classes of ratings
on labels of categories using the fully-connected neural network
as sentence vectors in each review are compressed
into an weighted average of them.
At the second step, the relations of text and sentences in a review
and categories are considered to classify it.

In the experiments,
And, from the result that the proposed method indicated better accuracy
than the comparative methods and the present method specialized
for sentiment classification on multiple categories,
it is found out that
the order of sentences in a review is important for sentiment classification
and PV-DM captures some sort of different features them
applied to a whole document and sentences in a review.
